Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-27 paper/structureScene.tex
write more IV. D

\subsection{Early vs. late temporal integration}
Owing to the scarcity of salient events in many natural soundscapes, fine-grained classification of auditory scenes is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate auditory scenes which share part of their semantic content, \eg a subway train from a subway station or a quiet street from a park.

A straightforward approach, known as early integration, consists in summarizing the multivariate time series of scattering coefficients over the full duration of the auditory scene, by retaining their average values only.
Going back to the definition of the scattering transform given in section \ref{sec:scattering}, this is equivalent to increasing the support $T$ of the low-pass filter $\boldsymbol{\phi}(t)$ up to infinity.

>>>>

\subsection{Early vs. late temporal integration}
Owing to the scarcity of salient events in many natural soundscapes, fine-grained classification of auditory scenes is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate auditory scenes which share part of their semantic content, \eg a train from a subway station or a quiet street from a park.
Depending on whether aggregation is performed in feature space or in decision space, the corresponding method is referred to as early or late integration.

A straightforward application of early integration consists in summarizing the multivariate time series of scattering coefficients over the full duration of the auditory scene, by retaining their average values only.
Going back to the definition of the scattering transform given in section \ref{sec:scattering}, this is equivalent to increasing the support $T$ of the low-pass filter $\boldsymbol{\phi}(t)$ up to infinity. With a slight abuse of notation, we denote by
\begin{equation}
\mathbf{S}\boldsymbol{x}(\gamma) =
\int_{-\infty}^{+\infty} \mathbf{S}\boldsymbol{x}(t,\gamma)\;\mathrm{d}t
\end{equation}
the summarized features.

In turn, late integration
